% original_resume.tex
\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.55in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\usepackage{xcolor} % For color
\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{fontawesome}
\usepackage[T1]{fontenc} % Use T1 font encoding

\name{Shivam Jha} % Your name

\address{
 \faPhone \hspace{0.1cm} \href{tel:+91 8003127994}{+91 8003127994} \\
 \faEnvelope \hspace{0.1cm} \href{mailto:Shivamjha.1299@gmail.com}{Shivamjha.1299@gmail.com} \\
 \faLinkedin \hspace{0.1cm} \href{https://linkedin.com/in/shivam-jha-0009/}{shivam-jha-0009} \\
 \faCode \hspace{0.1cm} \href{https://leetcode.com/Nightmare9}{Leetcode} \\
  \faCode \hspace{0.1cm} \href{https://www.codechef.com/users/nightmare_9}{CodeChef}
}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{##1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{##1}}
\renewcommand{\normalsize}{\fontsize{9}{3}\selectfont}

\begin{document}


%----------------------------------------------------------------------------------------
%	SUMMARY
%---------------------------------------------------------

\begin{rSection}{SUMMARY}
 \vspace{-2pt}
Full-Stack Software Engineer with nearly 3 years of experience specialising in React.js, Next.js, Node.js, TypeScript, and Python. I'm proficient in building microservices, web applications, scaling Backend, RESTful APIs, and cloud-native solutions on AWS.
\end{rSection}
%----------------------------------------------------------------------------------------
% WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
 \vspace{-5pt}
\begin{rSection}{WORK EXPERIENCE}

\textit{Software Engineer} \hfill December 2023 - Present\\
\textbf{Scale AI} (Contractual Role)\hfill \textit{Remote, US}
 \begin{itemize}
    \vspace{-1pt} % Adjust the space as needed
    \itemsep -3pt {} 
    \item Developed and maintained full-stack web applications using React.js, Next.js and TypeScript, implementing SSR and API routes to improve performance by 22\%.
    \item Built RESTful APIs using Node.js/Express and integrated third-party services, achieving 5/5 accuracy ratings in evaluation projects.
    \item Implemented responsive UI components with React hooks and context API, following modern frontend architecture principles.
    \item Created reusable component libraries and custom hooks, improving development efficiency across multiple projects.

    \item Optimized PostgreSQL database interactions to efficiently manage and query large datasets.
    \item Collaborated effectively with cross-functional teams across US time zones, demonstrating excellent remote work capabilities.
 \end{itemize}

\textit{Software Engineer} \hfill \textit{March 2023 - December 2023} \\
\textbf{Samsung R\&D Institute Bangalore} \hfill \textit{Bengaluru, India}
\begin{itemize}
    \vspace{-1pt}
    \itemsep -3.5pt {}
    \item Introduced a React Web-Chat App for 10,000+ users, improving internal communication and user experience.
    \item Revamped backend infrastructure with Node.js, Socket.IO, and Express, resulting in a 25\% improvement in application performance.
    \item Led containerization and deployment of 15+ microservices using Docker and Kubernetes, attaining 98\% service availability on AWS EKS clusters, efficiently handling 2x peak traffic volume.
    \item Implemented robust deployment, replication, auto-healing, and auto-scaling strategies for Kubernetes clusters, leveraging Kong gateway for API rate limiting and decreasing API latency by 15\%.
    \item Enhanced application security by integrating Bcrypt, JWT, OAuth, and upgrading encryption with Libsodium, significantly reducing unauthorized access attempts and addressing security vulnerabilities.
\end{itemize}


 
\textit{Software Development Engineer Intern} \hfill January 2022 - July 2022\\
\textbf{Amazon} \hfill \textit{Bengaluru, India}
 \begin{itemize}
    \vspace{-1pt} % Adjust the space as needed
    \itemsep -4pt {}
    \item Optimized large-dataset (800TB-1.5PB) computation time using Python, Ray, React, TypeScript \& Java, significantly boosting service efficiency and scalability.
    \item Improved Data Quality Standards, achieving 13\% monthly cost savings by streamlining calculations with Ray and enhancing data accessibility with Amazon DynamoDB.
    \item Developed a React front-end to visualise Marketplace tables Data Quality statistics, improving decision-making.
\end{itemize}


\end{rSection} 


%----------------------------------------------------------------------------------------
% PROJECTS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{PROJECTS}
\textbf{Paytm-mini} \hfill \textit{Side Project}
\begin{itemize}
    \vspace{-1pt} % Adjust the space as needed
    \itemsep -3pt {}
    \item Built full-stack payments app (TypeScript, React, Recoil, Vite, Tailwind) with reusable UI for transfers \& dashboard; secured with JWT auth (Node.js backend) \& Postman API validation.
    \item Deployed backend on AWS; built responsive features: debounced search, live balance, and validated transfers with error handling.
\end{itemize}
\end{rSection}




%----------------------------------------------------------------------------------------
% SKILLS SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}
\begin{itemize}
\itemsep -3pt {}
\item
\textbf{Programming Languages:} JavaScript, TypeScript, C++, Python, SQL, Java (Intermediate). \\
\vspace{1pt} % Adjust the vertical space as needed

\item
\textbf{Tools and Frameworks:} React.js, Next.js, Node.js, Express.js, Flask, Django, Socket.IO, Redis, GraphQL, HTML, Tailwind CSS, REST APIs, Redux/Recoil, JWT, OAuth, Docker, Kubernetes, Git, JIRA, Unit Testing, CI/CD. \\
\vspace{1pt} % Adjust the vertical space as needed

\item
\textbf{Cloud Skills:} AWS services (EKS, Lambda, S3, ECR, EC2, VPCs, SNS, SQS, API Gateway, DynamoDB), Microservices, GCP. \\
\vspace{1pt} % Adjust the vertical space as needed

\item
\textbf{Databases:} PostgreSQL, MongoDB, DynamoDB, Redis, Elastic Search, Firebase, Database Optimization. \\
\vspace{1pt} % Adjust the space as needed

\item
\textbf{Other:} Full-Stack Development, RESTful API Design, Backend Architecture, Agile, Code Reviews, System Design, Problem-Solving. \\
\end{itemize}
\end{rSection}

% ----------------------------------------------------------------------------------------
% EDUCATION SECTION
% ----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Indian Institute of Information Technology, Lucknow} \hfill {July 2018 - May 2022} \\
    % \vspace{-1pt} % Adjust the space as needed
    \itemsep -3pt {}
    \vspace{-5pt} % Adjust the space as needed
\begin{itemize}
    \item Bachelor of Technology in Information Technology, CGPA: 8.1. \\
    \vspace{-3pt} % Adjust the space as needed
    \item Coursework: Data Structures and Algorithms, Web Development, DBMS, OS, Computer Networks, System Design. \\
\end{itemize}

\end{rSection}

%----------------------------------------------------------------------------------------
% ACHIEVEMENTS SECTION
%----------------------------------------------------------------------------------------
 \vspace{-5pt}
\begin{rSection}{Achievements} 
\begin{itemize}
% \itemsep 1pt {} 
\vspace{3pt}
    \item Achieved \textbf{Samsung Pro Certified} status by passing the \textbf{SWC Pro Test} and receiving a bonus for this accomplishment.
    \item Ranked \textbf{132} globally in \textbf{CodeChef June LunchTime} 2021 among \textbf{4500+} contestants.
    \vspace{-3pt} % Adjust the space as needed
    \item Awarded a global rank of \textbf{1032} in \textbf{Google KickStart} 2021 Round D from \textbf{15000+} participants.
    \vspace{-3pt} % Adjust the space as needed
    \item Secured \textbf{9th} place globally in the Code Benders competition out of \textbf{900+} participants.
    \vspace{-3pt} % Adjust the space as needed
\end{itemize}
\end{rSection}

\end{document}